Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-12 longoutput.tex
Change a TODO
Move and work on gate set

@@

It is easier to check that it works and is Hermitian and works as expected by a unitary change of basis.

@@

I probably need to say even more on why this works but TODO I'll leave it for another day. There's also a closed form to the second smallest eigenvalue above that is apparently related to random walks but I can't find the source at the moment.

>>>>

\subsection{Properties of the gate set}

To this effect, we also define $G=$... TODO define set of tensors of XZI

@@

Next, we check that $H_{prop}\geq0$ by the following transform.

@@

TODO maybe say more about this.
